\LARGE \bf IMU-based pose-estimation for spherical robots with limited resources

### 2021-09-01 mfi21/ieeeconf/root.tex
small changes, suggested by reviewer

\section{Assumptions and Prelimitations}
\label{AssumptionsAndPrelimitations}
The presented approach works for any spherical robot which moves based on rotation and possesses IMUs.
Nevertheless, it requires multiple assumptions to be beneficial in comparison to existing approaches.
Some of these arise from the fundamental behavior of spherical robots and some more specific from the DAEDALUS project.
Therefore we state the following assumptions and requirements for the approach to become beneficial:

@@

But, as we described in the preliminary section, we can not take the input to locomotion control as a reference to pose estimation as the behavior is not linear or even predictable without exact knowledge of the surface.

@@

This does not meet the desired behavior as described in the prelimitations section~(\ref{AssumptionsAndPrelimitations}).

>>>>

\section{Assumptions and Prelimitations}
\label{sec:AssumptionsAndPrelimitations}
The presented approach works for any spherical robot which moves based on rotation and possesses IMUs.
Nevertheless, it requires multiple assumptions to be beneficial in comparison to existing approaches.
Some of these arise from the fundamental behavior of spherical robots and some more specific from the DAEDALUS project.
Therefore we state the following assumptions and requirements for the approach to become beneficial:

@@

But, as we described in the preliminary Section \ref{sec:AssumptionsAndPrelimitations}, we can not take the input to locomotion control as a reference to pose estimation as the behavior is not linear or even predictable without exact knowledge of the surface.

@@

This does not meet the desired behavior as described in the prelimitations Section~(\ref{AssumptionsAndPrelimitations}).
